Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-08 Paper.tex
\hyperlink{R__u}

\linkdest{transaction_receipt_R}{}\linkdest{tx_receipt_gas_used_R__u}{}The transaction receipt, $R$, is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_{\mathrm{u}}$, the set of logs created through execution of the transaction, \hyperlink{RLP_serialisation_of_a_sequence_of_other_items_R__l_math_def}{$R_\mathbf{l}$} and the Bloom filter composed from information in those logs, \hyperlink{RLP_serialisation_of_a_byte_array_R__b_math_def}{$R_{\mathrm{b}}$} and the status code of the transaction, $R_{\mathrm{z}}$:
\begin{equation}
R \equiv (R_{\mathrm{u}}, R_{\mathrm{b}}, R_{\mathbf{l}}, R_{\mathrm{z}})
\end{equation}

@@

The given \textbf{gasUsed} must correspond faithfully to the transactions listed: \hyperlink{H__g}{${B_{H}}_{\mathrm{g}}$}, the total gas used in the block, must be equal to the accumulated gas used according to the final transaction:
\begin{equation}
{B_{H}}_{\mathrm{g}} = \hyperlink{ell}{\ell}(\mathbf{R})_{\mathrm{u}}
\end{equation}

>>>>

\linkdest{transaction_receipt_R}{}\linkdest{tx_receipt_gas_used_R__u}{}\linkdest{R__u}The transaction receipt, $R$, is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_{\mathrm{u}}$, the set of logs created through execution of the transaction, \hyperlink{RLP_serialisation_of_a_sequence_of_other_items_R__l_math_def}{$R_\mathbf{l}$} and the Bloom filter composed from information in those logs, \hyperlink{RLP_serialisation_of_a_byte_array_R__b_math_def}{$R_{\mathrm{b}}$} and the status code of the transaction, $R_{\mathrm{z}}$:
\begin{equation}
R \equiv (R_{\mathrm{u}}, R_{\mathrm{b}}, R_{\mathbf{l}}, R_{\mathrm{z}})
\end{equation}

@@

The given \textbf{gasUsed} must correspond faithfully to the transactions listed: \hyperlink{H__g}{${B_{H}}_{\mathrm{g}}$}, the total gas used in the block, must be equal to the accumulated gas used according to the final transaction:
\begin{equation}
{B_{H}}_{\mathrm{g}} = \hyperlink{ell}{\ell}(\hyperlink{R__u}{\mathbf{R})_{\mathrm{u}}}
\end{equation}
